---
title: 'Kaggle: House Price Prediction'
author: "tiangsinf"
date: "9/23/2018"
output: 
  html_document: 
    keep_md: yes
---

```{r, Prelims, message = FALSE}
library(tidyverse)
library(ggplot2)

# import data
house_price <- read.csv("dataset/train.csv")
```

```{r, nooutput, results = 'hide'}
head(house_price, n = 10)
str(house_price) # 81 variables including id
```

## Dealing with Factors
Based on `data_description.txt`, `MSSubClass`, `OverallQual`, `OverallCond` columns should be ordinal factors instead of integers. The following chuck is to convert `MSSubClass` column to a factor.
Besides, there are others unordered factors that appears to be ordered include:
* LotShape
* Utilities
* LandSlope
* ExterQual
* ExterCond
* BsmtQual
* BsmtCond
* BsmtExposure
* BsmtFinType1
* BsmtFinType2
* HeatingQC
* KitchenQual
* Functional
* FireplaceQu
* GarageFinish
* GarageQual
* GarageCond
* PoolQC
* Fence
```{r}
# Convert MSSubClass
house_price$MSSubClass <- factor(house_price$MSSubClass, ordered = TRUE, levels = c(20, 30, 40, 45, 50, 60, 70, 75, 80, 85, 90, 120, 150, 160, 180, 190))

# Convert OverallQual
house_price$OverallQual <- factor(house_price$OverallQual, ordered = TRUE, levels = c(10, 9, 8, 7, 6, 5, 4, 3, 2, 1))

# Convert OverallQual
house_price$OverallCond <- factor(house_price$OverallCond, ordered = TRUE, levels = c(10, 9, 8, 7, 6, 5, 4, 3, 2, 1))
```

### Treating `NA` values.
Checking from `data_description.txt` certain `NA` values are not missing values. For example, the `NA` for `house_price$PoolQC` represent "No Pool" instead of missing value. Perhaps I should first convert these type of `NA` to a more meaningful values.
Columns with `NA` that are not missing values include:
* Alley - No alley access
* BsmtQual - No basement
* BsmtCond - No basement
* BsmtExposure - No basement
* BsmtFinType1 - No basement
* BsmtFinType2 - No basement
* FireplaceQu - No fireplace
* GarageType - No garage
* GarageFinish - No garage
* GarageQual - No garage
* GarageCond - No garage
* PoolQC - No pool
* Fence - No fence
* MiscFeature - No misc feature

```{r}
col_with_na <- sapply(house_price, function(x) any(is.na(x)))
names(house_price[col_with_na]) # list of columns with na values. Total 19 columns with na.
```



```{r, the dataset}
col_class <- sapply(house_price, class)
table(col_class) # 43 factor and 38 int columns

# Check columns with na value:
col_with_na <- sapply(house_price, function(x) any(is.na(x)))
names(house_price[col_with_na]) # list of columns with na values. Total 19 columns with na.

# Separating num and fac columns
int_col <- names(house_price[col_class == "integer"])
fac_col <- names(house_price[col_class == "factor"])

int_col_df <- house_price[, int_col][-1] # Subset integer columns and drop id
fac_col_df <- house_price[, fac_col]

View(head(fac_col_df, n = 20))
View(head(int_col_df, n = 20))
fac_levels <- sapply(fac_col_df, levels)

house_price %>%
    group_by(BsmtQual) %>%
    summarise(n = n())
```

```{r}

```

